Simulation Study: Varying Informativeness

### 2018-07-26 datasets/simulations/simulations-varyinginformativeness.Rmd
Add missing code in sim Rmd

```{r info00-run-simulation}
if (file.exists(info00_file)) {
    res <- readRDS(info00_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = info00_file)
}
```

>>>>

```{r info00-run-simulation}
if (file.exists(info00_file)) {
    res <- readRDS(info00_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = info00_file)
}
res_i <- lapply(res, `[[`, "informative")
res_u <- lapply(res, `[[`, "uninformative")
```
